Scalar on Function Regression

### 2022-01-06 Presentation/slides.tex
Update slides.tex
\hat{\beta} stuff...

		\begin{itemize}
			\item Near-infrared (NIR) spectroscopy enables fast diagnostics by using the NIR region of the electromagnetic spectrum
			\item Suited for field-monitoring / on-line analysis and diagnostics of e.g: prediction of octane ratings!

			\item Spectroscopy results in high-dimensional dataset.
			\item
			This set of measurements along a continuum can be viewed as set of smooth spectral curves
			\item
			Regression to determine relationship between octane rating and spectral curves
			\end{itemize}
	\end{frame}

@@

		Coefficients can then be estimated using theory from multivariate regression leading to an estimated coefficient vector $\hat{\beta}_L \in \mathbb{R}^L$.
	\end{frame}

	\begin{frame}{Estimation via Basis Representation}
		This can then be translated into an estimated coefficient function $\hat{\beta}(t)$ via:
	\end{frame}

>>>>

		\begin{itemize}
			\item Near-infrared (NIR) spectroscopy enables fast diagnostics by using the NIR region of the electromagnetic spectrum
			\item Suited for field-monitoring / on-line analysis and diagnostics of e.g: prediction of octane ratings!
			\item Spectroscopy results in high-dimensional dataset.

			\item
			This set of measurements along a continuum can be viewed as set of smooth spectral curves

			\item
			Regression to determine relationship between octane rating and spectral curves
			\end{itemize}
	\end{frame}

@@

		Coefficients can then be estimated using theory from multivariate regression leading to an estimated coefficient vector $\hat{\psi}_L \in \mathbb{R}^L$.
	\end{frame}

	\begin{frame}{Estimation via Basis Representation}
		This can be translated into an estimated coefficient function $\hat{\beta}(t)$:

		$$\hat{\beta}_L(t) = \sum_{j = 1}^{L} \hat{\psi}_{L,j} b_j(t)$$
		\vspace{0.2cm}

		This is dependent on...
		\begin{itemize}
			\item The functional basis $(b_j(t))_{j \in \mathcal{I}}$ for the estimation of $\beta(t)$
			\item The truncation parameter $L$
			\item (The functional basis used to approximate the observations)
			\item (The truncation parameter in the approximation of the observations)
		\end{itemize}
	\end{frame}
